---
title: "screen-stock-report"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  symbol: "GOOG"
  window_length: 60
  look_ahead_window: 60
  hold_days: 5
---

## Setup


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(quantmod)
library(TTR)
library(dygraphs)
library(knitr)
library(lubridate)

source("/home/kirk/Documents/projects/StockScreeningStrategies/src/R/screen-pattern-match.R")

my_ggplot <- function(plot_data, pattern) {
  
  ggplot(plot_data, aes(date, price)) + 
    geom_point() + 
    geom_line() + 
    geom_smooth() + 
    geom_point(aes_string("date", pattern), color = "red") + 
    geom_line(aes_string("date", pattern), color = "red") +
    geom_smooth(aes_string("date", pattern), color = "darkgreen") + 
    labs(title = pattern_period)
  
}

```

## Run Screen

```{r run_screen, echo = FALSE}


stockdata <- getSymbols(params$symbol, auto.assign = FALSE)


window_length <- params$window_length
look_ahead_window <- params$look_ahead_window
hold_days <- params$hold_days


screen_out <- screen_pattern_match(stockdata = stockdata,
                                   window_length = window_length,
                                   look_ahead_window = look_ahead_window,
                                   hold_days = hold_days,
                                   comparisons = 10,
                                   method = "percent",
                                   degree = 5,
                                   df = 5,
                                   span = 0.75)
```

## Creating Plot Data


```{r create_plot_data, echo = FALSE}
end <- NROW(screen_out$data)


plot_data <- data.frame(date = index(screen_out$data)[(end - (window_length - 1)) : end],
                        price = as.numeric(Cl(screen_out$data)[(end - (window_length - 1)) : end]),
                        pattern1 = as.numeric(Cl(screen_out$data)[screen_out$index[1]:(screen_out$index[1] + (window_length - 1))]),
                        pattern2 = as.numeric(Cl(screen_out$data)[screen_out$index[2]:(screen_out$index[2] + (window_length - 1))]),
                        pattern3 = as.numeric(Cl(screen_out$data)[screen_out$index[3]:(screen_out$index[3] + (window_length - 1))]),
                        pattern4 = as.numeric(Cl(screen_out$data)[screen_out$index[4]:(screen_out$index[4] + (window_length - 1))]),
                        pattern5 = as.numeric(Cl(screen_out$data)[screen_out$index[5]:(screen_out$index[5] + (window_length - 1))]),
                        pattern6 = as.numeric(Cl(screen_out$data)[screen_out$index[6]:(screen_out$index[6] + (window_length - 1))]),
                        pattern7 = as.numeric(Cl(screen_out$data)[screen_out$index[7]:(screen_out$index[7] + (window_length - 1))]),
                        pattern8 = as.numeric(Cl(screen_out$data)[screen_out$index[8]:(screen_out$index[8] + (window_length - 1))]),
                        pattern9 = as.numeric(Cl(screen_out$data)[screen_out$index[9]:(screen_out$index[9] + (window_length - 1))]),
                        pattern10 = as.numeric(Cl(screen_out$data)[screen_out$index[10]:(screen_out$index[10] + (window_length - 1))])
                        )


pred_data <- data.frame(date = (index(screen_out$data)[end]+1:100)[wday(index(screen_out$data)[end]+1:(look_ahead_window+hold_days))%in%2:6][1:(look_ahead_window+hold_days)],
                        price = NA,
                        pattern1 = as.numeric(Cl(screen_out$data)[(screen_out$index[1] + window_length):(screen_out$index[1] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern2 = as.numeric(Cl(screen_out$data)[(screen_out$index[2] + window_length):(screen_out$index[2] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern3 = as.numeric(Cl(screen_out$data)[(screen_out$index[3] + window_length):(screen_out$index[3] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern4 = as.numeric(Cl(screen_out$data)[(screen_out$index[4] + window_length):(screen_out$index[4] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern5 = as.numeric(Cl(screen_out$data)[(screen_out$index[5] + window_length):(screen_out$index[5] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern6 = as.numeric(Cl(screen_out$data)[(screen_out$index[6] + window_length):(screen_out$index[6] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern7 = as.numeric(Cl(screen_out$data)[(screen_out$index[7] + window_length):(screen_out$index[7] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern8 = as.numeric(Cl(screen_out$data)[(screen_out$index[8] + window_length):(screen_out$index[8] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern9 = as.numeric(Cl(screen_out$data)[(screen_out$index[9] + window_length):(screen_out$index[9] + (window_length + look_ahead_window + hold_days - 1))]),
                        pattern10 = as.numeric(Cl(screen_out$data)[(screen_out$index[10] + window_length):(screen_out$index[10] + (window_length + look_ahead_window + hold_days - 1))])
                             
                             
)

plot_data <- rbind(plot_data[,1:9], pred_data)


plot_data <- plot_data %>%
  mutate(
         pattern1_rescale = rescale_to_current(current_price = price, check_price = pattern1),
         pattern2_rescale = rescale_to_current(current_price = price, check_price = pattern2),
         pattern3_rescale = rescale_to_current(current_price = price, check_price = pattern3),
         pattern4_rescale = rescale_to_current(current_price = price, check_price = pattern4),
         pattern5_rescale = rescale_to_current(current_price = price, check_price = pattern5),
         pattern6_rescale = rescale_to_current(current_price = price, check_price = pattern6),
         pattern7_rescale = rescale_to_current(current_price = price, check_price = pattern7),
         pattern8_rescale = rescale_to_current(current_price = price, check_price = pattern8),
         pattern9_rescale = rescale_to_current(current_price = price, check_price = pattern9),
         pattern10_rescale = rescale_to_current(current_price = price, check_price = pattern10)
  )
         
         
```



## Candle Stick Graph

```{r dygraph_plot, echo = FALSE}
OHLC(stockdata) %>%
  dygraph() %>%
  dyCandlestick
```


## Pattern Compare {.tabset}

```{r all_patterns_ggplot,  echo = FALSE, eval = FALSE}
ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(span = 0.5) +
  geom_smooth(aes(x = date, y = pattern1_rescale), color = "darkgreen", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern2_rescale), color = "darkblue", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern3_rescale), color = "darkorange", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern4_rescale), color = "darkred", span = 0.5) + 
  geom_smooth(aes(x = date, y = pattern5_rescale), color = "darkgrey", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern6_rescale), color = "lightgreen", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern7_rescale), color = "lightblue", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern8_rescale), color = "orange", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern9_rescale), color = "pink", span = 0.5) +
  geom_smooth(aes(x = date, y = pattern10_rescale), color = "lightgrey", span = 0.5)
```


```{r create_text_rmd_old, eval = FALSE, include = FALSE}
src_text_rmd <- paste0("### Pattern{{idx}}", 
                       "\n",
                       "```{r}",
                       "\n",
                       "pattern_period <- paste0(index(screen_out$data[screen_out$index[{{idx}}]:(screen_out$index[{{idx}}] + (window_length -1))])[c(1,60)],collapse=' to ')",
                       "\n\n",
                       "ggplot(plot_data, aes(x = date, y = price)) + ",
                       "geom_point() + ",
                       "geom_smooth(aes(x = date, y = price)) + ",
                       "geom_point(aes(x = date, y = pattern{{idx}}_rescale), color = 'red') + ",
                       "geom_smooth(aes(x = date, y = pattern{{idx}}_rescale), color = 'darkgreen', span = 0.5) + ",
                       "labs(title = pattern_period)",
                       "\n\n",
                       "```",
                       "\n\n")

src <- lapply(1:10, function(idx) knit_expand(text = src_text_rmd))
```


```{r create_text_rmd}
src_text_rmd <- paste0("### Pattern{{idx}}", 
                       "\n",
                       "```{r}",
                       "\n",
                       "pattern_period <- paste0(index(screen_out$data[screen_out$index[{{idx}}]:(screen_out$index[{{idx}}] + (window_length -1))])[c(1,60)],collapse=' to ')",
                       "\n\n",
                       "my_ggplot(plot_data, pattern = paste0('pattern', {{idx}}, '_rescale'))",
                       "\n\n",
                       "```",
                       "\n\n")

src <- lapply(1:10, function(idx) knit_expand(text = src_text_rmd))
```


`r knit(text = unlist(src))`


<!--

### Pattern 1

```{r pattern1_ggplot, echo = FALSE, warning = FALSE}
idx <- 1

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes(x = date, y = price)) + 
  geom_point(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen") +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "lightgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 2

```{r pattern2_ggplot, echo = FALSE, warning = FALSE}
idx <- 2

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 3

```{r pattern3_ggplot, echo = FALSE, warning = FALSE}
idx <- 3

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 4

```{r pattern4_ggplot, echo = FALSE, warning = FALSE}
idx <- 4

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 5

```{r pattern5_ggplot, echo = FALSE, warning = FALSE}
idx <- 5

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 6

```{r pattern6_ggplot, echo = FALSE, warning = FALSE}
idx <- 6

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```

### Pattern 7

```{r pattern7_ggplot, echo = FALSE, warning = FALSE}
idx <- 7

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```


### Pattern 8

```{r pattern8_ggplot, echo = FALSE, warning = FALSE}
idx <- 8

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 9

```{r pattern9_ggplot, echo = FALSE, warning = FALSE}
idx <- 9

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```



### Pattern 10

```{r pattern10_ggplot, echo = FALSE, warning = FALSE}
idx <- 10

pattern_period <- paste0(
  index(screen_out$data[screen_out$index[idx]:(screen_out$index[idx] + (window_length - 1))])[c(1,60)], 
  collapse=" to ")

ggplot(plot_data, aes(x = date, y = price)) +
  geom_point() +
  geom_smooth(aes_string(x = "date", y = paste0("pattern", idx, "_rescale")), color = "darkgreen", span = 0.5) +
  labs(title = pattern_period)

```

-->