---
title: "scratch-notebook"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(googlesheets4)
library(tidyverse)
library(data.table)
library(magrittr)
library(quantmod)
library(TTR)
library(plotly)
library(igraph)
library(visNetwork)



data_path <- "~/Documents/projects/StockScreeningStrategies/data/"
backtest <- read_csv(paste0(data_path, "backtest-screen-pattern-match.csv"))
```


## helpers.R

```{r}
to_avg <- function(x) {
  sapply(x, function(y) mean(as.numeric(unlist(strsplit(y, ";")))), USE.NAMES = FALSE)
}


to_prop <- function(x) {
  sapply(x, function(y) mean(as.numeric(unlist(strsplit(y, ";"))) > 1), USE.NAMES = FALSE)
}


unique_patterns <- function(x) {
  
  sapply(x, function(y) {
    
    idx <- as.numeric(unlist(strsplit(y, ";")))
    sum(idx[2:10] - idx[1:9] > 1) + 1
    
  }, USE.NAMES = FALSE)

}

```



## Winning Strategy with old Back test

```{r}

backtest_old <- read_csv(paste0(data_path, "backtest-screen-pattern-match-old.csv")) %>%
  filter(monday_open > 0, friday_close > 0) %>%
  mutate(percent_change = friday_close / monday_open)


backtest_old_filter <- backtest_old %>% 
  filter(buy_date < "2019-03-26") %>%
  select(buy_date, sell_date, symbol, monday_open, friday_close, screen_type, 
         screen_avg_change, screen_prop_up, percent_change)

topn_old <- backtest_old %>%
      filter(screen_prop_up  == 1,
             screen_type == "ns", ## input$screen_type, 
             screen_avg_change > 1.1, ## input$screen_avg_change,
             monday_open < 1e6) %>% ## input$price_cutoff) %>%
      group_by(buy_date) %>% 
      arrange(-screen_avg_change) %>% 
      # slice_head(n = 1) %>% ## input$topn) %>% THIS BREAKS EVERYTHING
      top_n(n = 1) %>% ## input$topn
      group_by(buy_date) %>% 
      summarise(gross = sum(percent_change), total = n(), return = gross/total) %>% 
      filter(return > 0) %>% 
      ungroup %>%
      mutate(cumprod = round(cumprod(return), 4))

old_backtest_symbols <- unique(backtest_old_filter$symbol)
```


## Replicate with New Backtest Data

```{r}

backtest <- read_csv(paste0(data_path, "backtest-screen-pattern-match.csv")) %>%
  filter(monday_open > 0, friday_close > 0) %>%
  mutate(percent_change = friday_close / monday_open) %>%
  # filter(symbol %in% old_backtest_symbols) %>%
  mutate(screen_avg_change = to_avg( percent_change_window_hold ),  ## percent_change_present_hold
         screen_prop_up = to_prop( percent_change_window_hold )) %>%
  select(buy_date, sell_date, symbol, monday_open, friday_close, screen_type, 
         screen_avg_change, screen_prop_up, percent_change)


topn <- backtest %>%
  filter(screen_prop_up  == 1,
         screen_type == "ns", ## input$screen_type, 
         screen_avg_change > 1.1, ## input$screen_avg_change,
         monday_open < 1e6) %>% ## input$price_cutoff) %>%
  group_by(buy_date) %>% 
  arrange(-screen_avg_change) %>% 
  # slice_head(n = 1) %>% ## input$topn) %>%
  # slice_max(n = 1, order_by = -screen_avg_change) %>%  ## NOT THE SAME AS top_n
  ## top_n(n = 1) %>% ## input$topn  ## returns top N based off of last column (percent_change)
  group_by(buy_date) %>% 
  summarise(gross = sum(percent_change), total = n(), return = gross/total) %>% 
  filter(return > 0) %>% 
  ungroup %>%
  mutate(cumprod = round(cumprod(return), 4))

```





## Create Summaries For Different Parameter Settings

  - screen type
  - top N
  - screen percent change metric
  - price of stock (below a certain value)
  - unique number of patterns
  - norm value (below a certain value)


For each setting creating summary of how the screen method would do across all the weeks.

```{r}
screen_type <- c("percent", "poly", "legendre", "ns", "loess")
topn_cutoff <- 1:20
screen_metric <- c("percent_change_window_hold", "percent_change_window_holdlook",
                   "percent_change_present_hold", "percent_change_present_holdlook")
screen_change <- seq(1, 1.25, 0.05)
num_patterns <- 2:7
price_cutoff <- c(2, 5, 10, 20, 50, 100, 1000, 1e6)
# norm_cutoff <- 1:5

hypertune_out <- lapply(screen_type, function(st) {
  lapply(topn_cutoff, function(n) {
    lapply(screen_metric, function(sm) {
      lapply(screen_change, function(sc) {
        lapply(num_patterns, function(np) {
          lapply(price_cutoff, function(pc) {
       
## testing parameters     
# st <- "percent"
# n <- 1
# sm <- "percent_change_present_hold"
# sc <- 1.1
# np <- 5
# pc <- 1e6
            
            out <- backtest %>%
              rename(screen_change = ends_with(match = sm)) %>% ## screen_metric (sm)
              filter(monday_open > 0, friday_close > 0) %>%
              mutate(percent_change = friday_close / monday_open) %>%
              mutate(screen_avg_change = to_avg( screen_change ),
                     screen_prop_up = to_prop( screen_change ),
                     unique_patterns = unique_patterns( index )) %>%
              filter(screen_prop_up  == 1,
                     screen_type == st, ## screen_type (st)
                     unique_patterns >= np,  ## num_patterns (np)
                     screen_avg_change > sc, ## screen_change (sc)
                     monday_open < pc) %>% ## price_cutoff (pc)
              group_by( buy_date ) %>% 
              arrange( -screen_avg_change ) %>%
              slice_head( n = n ) %>%  ## topn_cutoff (n)
              group_by( buy_date ) %>% 
              summarise( gross = sum(percent_change), total = n(), return = gross/total ) %>% 
              ungroup %>%
              mutate(cumprod = round(cumprod(return), 4),
                     screen_type = st,
                     topn_cutoff = n,
                     screen_metric = sm,
                     screen_change = sc,
                     num_patterns = np,
                     price_cutoff = pc
                     ) 
            
            ## output backtest summary
            out
            
            
          }) %>% ## END: price_cutoff
            do.call(rbind, .)
          
        }) %>% ## END: num_patterns
          do.call(rbind, .)
        
      }) %>% ## END: screen_metric
        do.call(rbind, .)
      
    }) %>% ## END: screen_change
      do.call(rbind, .)
    
  }) %>% ## END: topn_cutoff
    do.call(rbind, .)
    
}) %>% ## END: screen_type
  do.call(rbind, .)


# 
# backtest %>%
#   rename(screen_change = ends_with(match = sm)) %>% ## screen_change
#   filter(monday_open > 0, friday_close > 0) %>%
#   mutate(percent_change = friday_close / monday_open) %>%
#   mutate(screen_avg_change = to_avg( percent_change_window_hold ),  ## percent_change_present_hold
#          screen_prop_up = to_prop( percent_change_window_hold ),
#          unique_patterns = unique_patterns( index )) %>%
#   # select(buy_date, sell_date, symbol, monday_open, friday_close, screen_type, 
#   #        screen_avg_change, screen_prop_up, percent_change) %>%
#         filter(screen_prop_up  == 1,
#              screen_type == input$screen_type, 
#              screen_avg_change > input$screen_avg_change,
#              monday_open < input$price_cutoff) %>%
#       group_by(buy_date) %>% 
#       arrange(-screen_avg_change) %>% 
#       slice_head(n = ) %>%
#       group_by(buy_date) %>% 
#       summarise(gross = sum(percent_change), total = n(), return = gross/total) %>% 
#       filter(return > 0) %>% 
#       ungroup %>%
#       mutate(cumprod = round(cumprod(return), 4))
# 
# 
# 
# 
# 
#     backtest %>%
# 
#       mutate(screen_avg_change = to_avg( screen_change ),  ## percent_change_present_hold
#              screen_prop_up = to_prop( screen_change )) %>%
#       select(buy_date, sell_date, symbol, monday_open, friday_close, screen_type, 
#              screen_avg_change, screen_prop_up, percent_change) %>%
#       filter(screen_prop_up  == 1,
#              screen_type == input$screen_type, 
#              screen_avg_change > input$screen_avg_change,
#              monday_open < input$price_cutoff) %>%
#       group_by(buy_date) %>% 
#       arrange(-screen_avg_change) %>% 
#       # slice_head(n = input$topn) %>%
#       top_n(n = input$topn) %>%
#       group_by(buy_date) %>% 
#       summarise(gross = sum(percent_change), total = n(), return = gross/total) %>% 
#       filter(return > 0) %>% 
#       ungroup %>%
#       mutate(cumprod = round(cumprod(return), 4))
# 

```


```{r}
st <- "poly"
sm <- "percent_change_present_hold"
np <- 2
sc <- 1
pc <- 1e6
n <- 1
  
backtest_summary <- backtest %>%
  rename(screen_change = ends_with(match = sm)) %>% ## screen_metric (sm)
  filter(monday_open > 0, friday_close > 0, screen_type == st) %>%
  mutate(percent_change = friday_close / monday_open) %>%
  mutate(screen_avg_change = to_avg( screen_change ),
         screen_prop_up = to_prop( screen_change ),
         unique_patterns = unique_patterns( index ),
         norm_avg_value = to_avg( norm_values )) %>%
  filter(screen_prop_up  == 1,
         screen_type == st, ## screen_type (st)
         unique_patterns >= np,  ## num_patterns (np)
         screen_avg_change > sc, ## screen_change (sc)
         monday_open < pc) %>% ## price_cutoff (pc)
  group_by( buy_date ) %>%
  arrange( -screen_avg_change ) %>%
  slice_head( n = n ) %>%  ## topn_cutoff (n)
  group_by( buy_date ) %>%
  summarise( gross = sum(percent_change), total = n(), return = gross/total ) %>%
  ungroup %>%
  mutate(cumprod = round(cumprod(return), 4),
         screen_type = st,
         topn_cutoff = n,
         screen_metric = sm,
         screen_change_cutoff = sc,
         num_patterns = np,
         price_cutoff = pc)




```


### SMA, MACD, RunCorr

  - Maybe use EMA

```{r}
workingdata <- cbind(quantmod::OHLC(stockdata),
                     TTR::SMA(quantmod::Cl(stockdata), n = 50),    
                     TTR::SMA(quantmod::Cl(stockdata), n = 200),
                     TTR::MACD(quantmod::Cl(stockdata)),
                     TTR::runCor(1:NROW(stockdata), TTR::SMA(quantmod::Cl(stockdata), n = 50), n =10)
                               ) %>% as.data.frame
colnames(workingdata) <- c("Open", "High", "Low", "Close", "SMA50", "SMA200", "MACD", "MACDsignal", "runcorr")

workingdata <- workingdata %>%
    dplyr::mutate(Date = as.Date(index(stockdata)),
                  SMA50above200 = as.numeric(SMA50 > SMA200),
                  MACDAboveSignal = as.numeric(MACD > MACDsignal),
                  runcorPos = as.numeric(runcorr > 0),
                  Position = as.numeric(SMA50above200 + MACDAboveSignal + runcorPos == 3)
    ) %>%
    ts %>%
    as.xts
  
  index(workingdata) <- index(stockdata)
```

